Generalized Tractability

### 2023-03-12 GeneralizedTractability_230310.tex
Updates from Overleaf
Fred M2 2023 Mac Updates

\begin{proof}
\textbf{Sufficient condition:}\newline
We make the first part of the argument in some generality so that it can be reused in the proof of Theorem \ref{thm_main_tract2} for tractability.  Given that $T$ is increasing in its arguments, we have the following equivalent expression for the complexity:
    \begin{equation} \label{eq:comp_equiv}
    \comp(\varepsilon, d) &= \min \{n \in \natzero : \lambda_{n+1, d} \le \varepsilon\} = \min \biggl\{n \in \natzero : \frac{1}{T(\lambda_{n+1,d}^{-1},d',\vp)}\le \frac{1}{T(\varepsilon^{-1},d',\vp) }\biggr\},
\end{equation}
for any $d' \in \naturals$.

@@

For $\varepsilon$ taking on all positive values, $j(\varepsilon,d,\vp)$ takes on all values greater than or equal to $j(\infty,d,\vp)$, so
\[
j\le C_{\vp}\, T(\varepsilon^{-1},d,\vp)+1 \le C_{\vp} T(\lambda_{j,d}^{-1},d,\vp)+1, \qquad \forall j \ge j(\infty,d,\vp).
\]
This implies via our technical assumption \eqref{eq:ptauassume} that
\begin{equation*}
	K_{\vp,\tau}\,T (\lambda_{j,d}^{-1},1,\tau \vp) \ge
	[T(\lambda_{j,d}^{-1},1, \vp)]^\tau
	\ge
	\left[\frac{(j-1)}{C_{\vp}}\right]^\tau \qquad \forall j \ge j(\infty,d,\vp)
\end{equation*}
Summing both sides of the inequality yields and noting that $L(\vp) \le L(\tau\vp)$, it follows that
\begin{multline*}
	\sup_{d\in\naturals} \sum_{j=L(\tau\vp)}^\infty \frac{1}{T (\lambda_{j,d}^{-1},1, \tau \vp)} \le
	\sup_{d\in\naturals} \sum_{j=L(\vp)}^\infty \frac{1}{T (\lambda_{j,d}^{-1},1, \tau \vp)} \\
	\le K_{\vp,\tau}\, C_{\vp}^\tau
	\sum_{j=L(\vp)}^\infty \frac{1}{(j-1)^\tau} \le
	K_{\vp,\tau}\, C_{\vp}^\tau\, \zeta (\tau) < \infty,
\end{multline*}
where $\zeta$ denotes the Riemann zeta function.
This yields \eqref{eq:strong_tractiff3} with $p$ replaced by $\tau p$, and so we see the necessity of $\eqref{eq:strong_tractiff3}$.

We know that
\[
\lambda_{\comp(\varepsilon,d)+1,d}\le \varepsilon.
\]
Since the eigenvalues $\lambda_{j,d}$ are non-increasing, we have
\begin{equation}\label{eq:lambda_K4}
\lambda_{\lfloor C_{\vp}\, T(\varepsilon^{-1},d,\vp)\rfloor +1,d}\le \varepsilon.
\end{equation}
Let
\[
j=j (\varepsilon):= \lfloor C_{\vp}\, T(\varepsilon^{-1},d,\vp)\rfloor +1.
\]
If we vary $\varepsilon\in (0,\infty)$, we see that $j=j_d^*, j_d^*+1, j_d^*+2,\ldots$, where
\[
  j_d^*=\lfloor C_{\vp}\, T(0,d,\vp)\rfloor +1
\]
Note that
\[
j\le C_{\vp}\, T(\varepsilon^{-1},d,\vp) +1.
\]
Due to our assumptions, we know that
$T(\cdot,d,\vp)$ is increasing in the first argument if
we keep $p$ and $q$ fixed.

Then, by \eqref{eq:lambda_K4},
\[
j \le C_{\vp}\, T(\varepsilon^{-1},d,\vp) +1 \le C_{\vp}\, T(\lambda_{j,d}^{-1},d,\vp) +1,
\]
and the latter chain of inequalities holds for all $j\ge j_d^*$.

This implies
\[
T(\lambda_{j,d}^{-1},d, \vp) \ge \frac{j-1}{C_{\vp}}.
\]
This, in turn, implies, for any $\tau>1$, that
\[
 (T(\lambda_{j,d}^{-1},d,\vp))^\tau \ge \frac{(j-1)^\tau}{C_{\vp}^\tau},
\]
which yields
\[
 K_{\vp,\tau}\, T (\lambda_{j,d}^{-1},d,\tau p,\tau q) \ge (T(\lambda_{j,d}^{-1},d, \vp))^\tau
 \ge \frac{(j-1)^\tau}{C_{\vp}^\tau}.
\]
This then implies
\[
\sum_{j=j_d^*}^\infty \frac{1}{T(\lambda_{j,d}^{-1},d, \tau p,\tau q)}
\le K_{\vp,\tau}\, C_{\vp}^\tau \sum_{j=j_d^*}^\infty \frac{1}{(j-1)^\tau}
\peter{\le K_{\vp,\tau}\, C_{\vp}^\tau \, \zeta(\tau)}
<\infty.
\]
\peter{
Consequently,
\[
\sup_{d\in\naturals} \sum_{j=j_d^*}^\infty \frac{1}{T(\lambda_{j,d}^{-1},d, \tau p,\tau q)} \le K_{\vp,\tau}\, C_{\vp}^\tau \, \zeta(\tau) < \infty.
\]
}
Note now that, \peter{for any $d\in\naturals$,}
\[
 j_d^* = \lfloor C_{\vp}\, T(0,d,\vp)\rfloor +1 \le \lfloor C_{\vp}^\tau\, T(0,d,\tau p,\tau q)\rfloor +1.
\]
So, there exists $L(\tau p,\tau q)$ such that
\[
\peter{\sup_{d\in\naturals}}\,\, \sum_{j=\lceil L(\tau p,\tau q) T(0,d,\tau p,\tau q)\rceil}^\infty \frac{1}{T(\lambda_{j,d}^{-1},d, \tau p,\tau q)}<\infty.
\]

>>>>

\begin{proof}
\textbf{Sufficient condition:}\newline
We make the first part of the argument in some generality so that it can be reused in the proof of Theorem \ref{thm_main_tract2} for tractability.  Given that $T$ is increasing in its arguments, we have the following equivalent expression for the complexity:
    \begin{equation} \label{eq:comp_equiv}
    \comp(\varepsilon, d) = \min \{n \in \natzero : \lambda_{n+1, d} \le \varepsilon\} = \min \biggl\{n \in \natzero : \frac{1}{T(\lambda_{n+1,d}^{-1},d',\vp)}\le \frac{1}{T(\varepsilon^{-1},d',\vp) }\biggr\},
\end{equation}
for any $d' \in \naturals$.

@@

For $\varepsilon$ taking on all positive values, $j(\varepsilon,d,\vp)$ takes on all values greater than or equal to $j(\infty,d,\vp)$, so
\[
j\le C_{\vp}\, T(\varepsilon^{-1},d,\vp)+1 \le C_{\vp} T(\lambda_{j,d}^{-1},d,\vp)+1, \qquad \forall j \ge j(\infty,d,\vp).
\]
This implies via our technical assumption \eqref{eq:ptauassume} that
\begin{equation*}
	K_{\vp,\tau}\,T (\lambda_{j,d}^{-1},d,\tau \vp) \ge
	[T(\lambda_{j,d}^{-1},d, \vp)]^\tau
	\ge
	\left[\frac{(j-1)}{C_{\vp}}\right]^\tau \qquad \forall j \ge j(\infty,d,\vp)
\end{equation*}
Summing both sides of the inequality yields and noting that $L(\vp) \le L(\tau\vp)$, it follows that
\begin{multline*}
	\sup_{d\in\naturals} \sum_{j=j(\infty,d,\vp)}^\infty \frac{1}{T (\lambda_{j,d}^{-1},d, \tau \vp)} \le
	\sup_{d\in\naturals} \sum_{j=j(\infty,d,\vp)}^\infty \frac{1}{T (\lambda_{j,d}^{-1},d, \tau \vp)} \\
	\le K_{\vp,\tau}\, C_{\vp}^\tau
	\sum_{j=j(\infty,d,\vp)}^\infty \frac{1}{(j-1)^\tau} \le
	K_{\vp,\tau}\, C_{\vp}^\tau\, \zeta (\tau) < \infty,
\end{multline*}
where $\zeta$ denotes the Riemann zeta function.
This yields \eqref{eq:strong_tractiff3} with $p$ replaced by $\tau p$, and so we see the necessity of $\eqref{eq:strong_tractiff3}$.

Note now that, \peter{for any $d\in\naturals$,}
\[
 j_d^* = \lfloor C_{\vp}\, T(0,d,\vp)\rfloor +1 \le \lfloor C_{\vp}^\tau\, T(0,d,\tau p,\tau q)\rfloor +1.
\]
So, there exists $L(\tau p,\tau q)$ such that
\[
\peter{\sup_{d\in\naturals}}\,\, \sum_{j=\lceil L(\tau p,\tau q) T(0,d,\tau p,\tau q)\rceil}^\infty \frac{1}{T(\lambda_{j,d}^{-1},d, \tau p,\tau q)}<\infty.
\]
